\section{Reflections and Results}\label{reflections and results}
In this last section we will briefly reflect on the project, what we have
done and then we will move on to the results of our simulations and what can
possibly interpreted from that.

\subsection{Reflection}\label{reflection}
In this project we have used fuzzy logic to implements fuzzy rules which have
controlled simulated mice. The challenge with this project has been how to
represent the fuzzy logic in a runtime structure. With this in place most of
the pieces was done, the inference mechanisms then just had to do their job
and get the final output done. When creating the runtime structure we had to
think about how to get different rules to work together, but when we managed
to create conditional statements which could be weaved together it fell into
place.

\subsection{Results}\label{results}
From what we have seen in a number of different runs, the rules work
quite well. The challenge is to create "intelligent" fuzzy rules. In some
sense this is where our project is lacking, we have devoted much time to
get the fuzzy logic up and running ,and we have used some time to get the
simulation to work. We can easily see that the rules we have work, and we
can see that the inference and everything work together, but to call
it intelligent is a stretch.

In the different runs we can see that our rules fire, by seeing the mice
hunt and flee from enemies. We can see that sometimes no action is selected
and mice start fighting even though that might not have been the brightest thing
to do. Since the area is quite limited, much fighting is going on at the start
because no mice really cares about what is happening, but when the dust settles
and there are only a few mice left, we can see that the strong start hunting
the weak. Sometimes we see the weak try to flee, and sometimes they try to
fight. When this is happening most of the behavior is down to the minimalistic
rules that we have used. With more advanced rules, more "intelligent" behavior
should be observed.

We have laid the foundation of what have been a very good fuzzy logic
implementation which has proven it self through our simulations.

\subsection{Future work}\label{future work}
There are many aspects of our fuzzy logic which can be improved. Chief among
them is improved parsing. What our implementation lacks is the power to
parse arbitrarily created if statements, in its current form we can do what
has been required of us, but it is not as good as it can be.

We would also like to improve how rules are parsed using Mamdani inference. As
it stands now, we have some restrictions that can hold the inference back compared
to what it should be able to do. The Sugeno inference works very well, much because
it's easier to implement, but also because our technique was a bit more elegant.
